\noindent{\Large\bf HNN extensions: group tools}

\bigskip
\hrule\hrule\hrule

\begin{enumerate}

\item Is G1 abelian?

\item Is G1 nilpotent?

\item Is G1 polycyclic?

\item Is G1 solvable?

\item Is G1 finite?

\item Is G1 automatic?

\item Is G1 hyperbolic?

\item Is G1 free?

\item Is G1 metric small cancellation?

\bigskip
\hrule\hrule\hrule

\item Compute the order of G1

\item Compute the center of G1

\item Compute the canonical decomposition of G1 abelianized

\item Compute a nilpotent quotient of G1

\item Compute the quotient of two successive terms of the lower central
series of G1

\item Compute a Schreier system of representatives for the elements of G1

\item Compute an integral homology group of G1

\bigskip
\hrule\hrule\hrule

\item Find an amalgamated product decomposition of G1

\item Find an HNN-extension decomposition of G1

\item Find a permutation representation of G1 when G1 is finite

\bigskip
\hrule\hrule\hrule
\item Find a finite rewriting system for G1

\bigskip
\hrule\hrule\hrule

\item Find an endomorphism of G1

\item Find an automorphism of G1

\item Find an IA-automorphism of G1

\item Find an automorphism of G1 of finite order

\bigskip
\hrule\hrule\hrule
\item Enumerate words of G1

\subitem Number of words
\subsubitem The generic word in the enumerator

\hskip 2.0in    x

\subsubitem Enumerate randomly
\subsubitem Enumerate totally
\subsubitem Enumerate using normal distribution
\subsubitem Enumerate using uniform distribution
\subsubitem Maximal length of words
\bigskip
\subitem Make a list from the word enumerator
\subsubitem Tool1: Extract words of a given length
from list of words - parameters: Minimal and maximal length
\subsubitem Tool2: Extract trivial words from list - parameters: none
\subsubitem Tool3: Extract central words from list - parameters: none
\bigskip
\item Enumerate subgroups of G1
\subitem Number of subgroups
\subitem Maximal number of generators
\subsubitem Enumerate randomly
\subsubitem Enumerate totally
\subsubitem Enumerate using normal distribution
\subsubitem Enumerate using uniform distribution
\subsubitem Maximum length of words
\bigskip
\subitem Make list
\bigskip
\item Enumerate relators of G1
\subitem Number of relators
\subsubitem Enumerate using normal closure
\subsubitem Enumerate using uniform distribution
\subsubitem Maximum length of conjugates
\subsubitem Number of factors
\subitem Make list

\bigskip
\item Enumerate endomorphisms of G1
\subitem Total enumeration
\subsubitem Number of endomorphisms

 \bigskip
\item Enumerate automorphisms of G1
\subitem Total enumeration
\subsubitem Number of automorphisms

\bigskip
\item Enumerate IA-automorphisms of G1
\subitem Total enumeration
\subsubitem Number of IA-automorphisms

\bigskip
\item Enumerate automorphisms of G1 of finite order
\subitem Total enumeration \subsubitem Number of automorphisms
\bigskip
\hrule\hrule\hrule

\item Delete selected objects and dependencies

\bigskip
\hrule\hrule\hrule

\item
Synopsis

\bigskip
\hrule\hrule\hrule

\end{enumerate}
